%-------------------------
% Resume in Latex
% Original Author : Sourabh Bajaj
% License : MIT
%------------------------

% Header taken from LaTeX template :
% Copyright (C) 2019 by Cheng XU <copyright@xuc.me>




\documentclass[letterpaper,11pt]{article}


\RequirePackage[fixed]{fontawesome5}



\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small #3} & {\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      {\small#1} & {\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}





%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{minipage}[c]{.4\linewidth}
    {\textbf{\Huge Harrison Button \\ \small{He/Him} }}%
\end{minipage}%
\begin{minipage}[c]{.6\linewidth}
    \begin{flushright}
        \faIcon{phone}~0433 931 043 \hspace{1pt} \faIcon{envelope}~harrisonsbutton@gmail.com \\
        \faIcon{linkedin}~linkedin.com/in/harrisonbutton \\ 
        \faIcon{github}~github.com/ignorant-fool
    \end{flushright}
\end{minipage}

%-----------EDUCATION-----------------
%ss\section{Education}
  %\resumeSubHeadingListStart
%    \resumeSubheading{The University of Western Australia}{}
%    {Master of Data Science}{July 2022 - Current}
  % \resumeSubheading{The University of Queensland}{}
  %  {Bachelor of Science (Honours) in Exploration Geophysics}{Feb. 2019 - Nov. 2020}
 %   \resumeSubSubheading{\hspace{1em} Thesis title: Linear inversion of seismic refraction amplitudes for near-surface velocity control.}{}
%      \begin{itemize}
%        \resumeItem{}{Thesis Title:    Linear inversion of seismic refraction amplitudes for near-surface velocity control.}
%      \end{itemize}\vspace{-5pt}
 %   \resumeSubSubheading
 %     {Bachelor of Mathematics / Science in Statistics and Geological Sciences (Extended)}{Feb. 2014 - Nov. 2018}
    
%  \resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
    {The University of Western Australia}{}
    {Graduate Certificate in Data Science}{Jul. 2022 -- Sep. 2023}
\resumeSubheading
    {The University of Queensland}{}
    {Bachelor of Science (Honours) in Exploration Geophysics}{Feb. 2019 -- Nov. 2020}
\resumeSubSubheading
    {Bachelor of Mathematics / Science in Statistics and Geological Sciences (Extended)}{Feb. 2014 -- Nov. 2018}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Rio Tinto Exploration}{} 
      {Geodata Scientist - Analyst II}{Jan. 2023 -- Present}
      \resumeItemListStart
        \resumeItem{}
            {Utilized Docker and AWS cloud computing services to scale-up internal R\&D projects, unlocking new capabilities in large-scale geophysical modelling for target generation and prioritization.}
        \resumeItem{}
            {Contributed to the full stack development of an image similarity application, including custom geoscientific visualizations and automated deployment through GitHub Actions.}
        \resumeItem{}
            {Helped manage an internal Posit Connect server with over 100 users from the regional exploration teams, and also provided general R expertise to citizen data scientists throughout the entire Rio Tinto company.}
      \resumeItemListEnd
      \resumeSubSubheading
        {Geodata Scientist - Analyst I}{Aug. 2021 -- Dec. 2022}
      \resumeItemListStart
        \resumeItem{}
            {Implemented recently published machine learning models for ore-body knowledge and target generation, highlighting new areas of prospective mineralization to the regional exploration teams.}
        \resumeItem{}
            {Automated GIS workflows and forward-looking economic simulations, saving hours of manual work per month.}
        \resumeItem{}
            {Collaborated with internal and external partners to produce data science products and applications for a global user base.}
      \resumeItemListEnd
    \resumeSubSubheading
     {Vacation Student - Geophysics}{Nov. 2020 -- Aug. 2021}
     \resumeItemListStart
        \resumeItem{}
          {Completed routine analysis of geophysical, geochemical, and petrophysical data for target generation in the Mt Isa (Cu-Au) and Pilbara (Fe ore) regions.}
        \resumeItem{}
          {Compiled project-wide and state-wide data sets.}
        \resumeItem{}
          {Supervised both airborne and ground geophysical surveys undertaken by geophysical contractors.}
     \resumeItemListEnd

    \resumeSubheading
      {The University of Queensland}{}
      {Tutor, School of Mathematics and Physics}{Jul. 2017 -- Nov. 2020}
      \resumeItemListStart
        \resumeItem{}
          {Tutored a wide range of introductory and advanced courses to specialist and non-specialist students. Select courses include DATA7202 "Statistical Methods for Data Science", STAT3006 "Statistical Learning", and STAT3500 "Problems and Applications in Modern Statistics".}
      \resumeItemListEnd

    \resumeSubheading
      {Santos}{}
      {Vacation Student - Geomechanics}{Nov. 2017 -- Feb. 2018}

    \resumeSubheading
      {Origin Energy}{}
      {Vacation Student - Exploration and New Resources}{Nov. 2016 -- Feb. 2017}

\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming: }
      {Knowledgeable in Python, R, \LaTeX. Basics in Fortran, Matlab, VBA, SQL, C.}
    \resumeSubItem{Geoscientific Software: }
      {Oasis Montaj, ioGas, ModelVision, Geoscience Analyst, ArcGIS Pro (including ArcPy).}
    \resumeSubItem{Other: }
      {AWS, Dash, Git, Jira, R Shiny, Posit Connect, Linux, Microsoft Excel.}
  \resumeSubHeadingListEnd

%
%--------MEMBERSHIPS------------
\section{Professional Memberships}
  \resumeSubHeadingListStart
    \resumeSubItem{Australian Society of Exploration Geophysicists: }
      {Graduate Member}
    \resumeSubItem{Australian Institute of Geoscientists: }
      {Graduate Member}
  \resumeSubHeadingListEnd

%--------MEMBERSHIPS------------
\section{Hobbies}
  \resumeSubHeadingListStart
    \resumeSubItem{}
      {Playing and seeing live music; collecting vinyl records; tinkering with computers; stationery; reading manga.}
  \resumeSubHeadingListEnd




%-------------------------------------------
\end{document}
